---
output:
  github_document: default
  html_notebook: default
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# pam

The goal of the pam package is to provide a set of functions to easily process monitoring-pam data, in order to obtain parameters such as:

 * Photochemical quenching (PQ)

 * Maximum PQ

 * Non-photochemical quenching (NPQ)

 * Sustained component of NPQ (NPQs)

 * Reversible component of NPQ (NPQr)

 * Yield of NPQ

 * Yield of NPQs

 * Yield of NPQr

 * Yield of photochemistry

 * Yield of fluorescence and basal thermal energy dissipation

 * Yield of fluorescence

 * Relative light saturation of photosynthesis
 
 * maximum PSII value

 * Reference maximal fluorescence

 * Reference minimal fluorescence

 * Maximum PSII value at night 

 * Night minimal fluorescence

 * Night maximal fluorescence




### How to install:


```{r, eval = FALSE}
# update.packages()

if(!(require("devtools"))){install.packages("devtools")}
library(devtools)

install_github("davidmartini90/pam")

```

### How to use:

```{r, eval = FALSE}
library(pam)
library(dplyr)

example_data

# adding acquisition and reference parameters and plotting Fmr and For
example_data %>%
  add_acquisition(
    start_of_night = "20:40",
    end_of_night = "05:00",
    date_format = "mdy"
  ) %>%
  add_reference() %>%
  plot_reference_parameters()

# adding acquisition, reference parameters and 
example_data %>%
  add_acquisition(
    start_of_night = "20:40",
    end_of_night = "05:00",
    date_format = "mdy"
  ) %>%
  add_reference() %>%
  add_pam_parameters() %>% 
  glimpse()
```

### How to read the functions documentation:

```{r, eval = FALSE}
library(pam)

?add_acquisition
?add_reference
?plot_reference_parameters
?add_pam_parameters

```


contact:  dmartini@bgc-jena.mpg.de

